Background for transient faults in asynchronous circuits

### 2019-04-15 draft_together3.tex
after major DD change added two sections

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Traces and circuit equivalence}
We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.  Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.  To solve this problem we add C-elements to synchronize the two versions of the same signal.  In the rest of this chapter we define a way to compare two circuits and to show their equivalence.  Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.  Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\

Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.  Different paths can occur because each state may have multiple alternative transitions from that state.  We record the succession of states and transitions by the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: 0\ldots n-1 \to S$ and $n \in \mathbb{N}$.
 Also every pair of consecutive states are transitions such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$.  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
Thus a circuit as well as its underlying state graph corresponds to a set of traces.  
set of initial states
and state graph has a set of traces
Our definition of trace includes the case where there is only one transition from each state of a state graph, that is, a linear state graph.  \\
%add finite traces
% all states or just the state graph ones

Given two circuits, how can we determine when their basic functionality is the same even if they are implemented with different gates and circuit elements?  We define a notion of equivalence between two circuits.  We want the underlying state graph representation of the circuits to be equivalent.  However only the signals and the sequence of its transitions from the circuit is observable.  In other words the trace is observable.  Thus we define circuits as equivalent if the set of traces of the two circuits are the same. [We use the assumption that if the set of traces are equal then the state graph is equal.]
\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B (up to a permutation of the variable names).  In other words, if it is possible to pair wires in A and B in such a way that $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
\end{definition}
%good enough for now, do I need if and only if? <-NO, xxx if xxx in math lingo is iff

@@

We make a circuit fault tolerant by the following transformation on an existing semi-modular circuit: make a duplicate copy of the logic blocks of each wire $w$.  We label the duplicated logic blocks as belonging to circuit A or circuit B.  Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.  We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ and $c1^B$, $c2^B$, $c3^B$ for circuits A and B respectively.  In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and are inputs to two C-elements outputting $c2^A$ and $c2^B$.  These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.  These are then the inputs to the third layer of C-elements outputting $w^A$ and $w^B$.  We can label one of the final C-element outputs as $w^A$ and the other output as $w^B$.  These then connect to other logic blocks in circuit A and circuit B respectively.  Note that at some steps of the labelling which side is A and B can be somewhat arbitrary because the outputs of pairs of C-elements with the same inputs are symmetric.  The symmetry is broken by connecting the final output $w^A$ to all its circuit A gate inputs and $w^B$ to all its circuit B gate inputs.  All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie. all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{circuitforproof3}
  \caption{Duplicating the original logic for each output wire and adding 3 layers of C-elements}
  \label{fig:dupscheme}
\end{figure}

Because the circuit transformation introduces extra wires, we want to define a correspondence to compare states of the original circuit with those of the A-half and B-half of the fault tolerant circuit.  A state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.  Half of those bits are obviously from the A half of the circuit and half are from the B half.  The state graph for a fault tolerant circuit is defined on this combined state.  We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.  The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.  The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are ignored.  We extend $h^A$ pointwise to traces, in other words, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.  %not sure if I want the mapping to be from variable to variable or specific state to state
%For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
The resulting trace may have successive repeated states and we delete the neighboring repeats to obtain a valid trace on the shortened list of wires.  %do I need to define all the new transitions in duplicated circuit?  maybe
\\

\section{Normal operation analysis}
To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similar to the original circuit under normal operation.  That is, after applying a mapping of $h^A$, the set of traces of the resultant circuit and that of the original circuit are equal.  And likewise after applying a mapping of $h^B$.  This goal is achieved by proving several Lemmas. Lemma 1 shows for each half of a circuit, if a transition occurs it must follow the transitions of the state graphs of the original circuit.  This property is independent of the signals on the other half circuit which is significant later in proving fault tolerance under a single transient fault as the half without the fault will transition as normal by Lemma 1.  %as long as it does not violate digital abstraction
One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\

Note that Lemma 1 does not guarantee that a transition always exists from a given state so Lemma 2 is needed to show that a transition always exists and as a consequence the circuit cannot deadlock.  These two Lemmas combine together to show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace

The internal wires in the logic blocks which are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.  The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.  The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.  This arises from the original synthesis method to synthesize the circuit from an underlying state graph.  
Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.  The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.  Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.  %maybe needs an example
Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.  Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions. \\%newly added

The initial wire values of a circuit is equally important.  In the original circuit, all states of a trace are states in the underlying state graph.  In particular the initial wire values corresponding to the initial state $s$ must also be a state in the underlying state graph.  In addition, as mentioned in the previous paragraph, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.   The fault tolerant circuit must be initialized in a similar way.  We introduce one possible initialization for the fault tolerant circuit based on the initialization of the original circuit.  This covers how to initialize both the duplicated copies as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.  The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s. The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.  Given these we will show how to define a corresponding initial state in the duplicated circuit.  %should I delete intermediate?
\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed as follows.  Given any state in the original circuit state graph $s \in S$, assume that there exists initial wire values that correspond to $s$.  In addition, for each wire $w$, the internal wire values within the logic block of $w$ are semi-modularity consistent.  Construct the valid initial state by copying the internal wire values to corresponding internal wires in the A half circuit.  Then assign the value $w$ to appropriate wires in the A half circuit such as $w=c1^A=c2^A=c3^A=w^A$. The same construction can be applied for the B half circuit as well.
\end{definition}
%\textbf{
For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.  I will not include this assumption in the following lemma definitions to avoid complicated wording.  %}  
The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\

This leads to Lemma 1, with the description and proof as follows:

\begin{lemma}[1]
If $\sigma$ is the trace of the fault tolerant circuit, then in the A half:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.  And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
\end{itemize}

The trace $\sigma$ can be finite or infinite in length.  
%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
By symmetry this is also true for the B half if we exchange A and B in the statement above.

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
\begin{proof}
Without loss of generality we prove that this property holds for the A half, the same reasoning can then be applied to the B half.  We prove this Lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
\begin{itemize}
\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  Also a wire $w$ is unexcited if and only if none of the four excited conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.  This case can also interpreted as the logic block being excited.  Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.  As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.  By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.  This shows the valid initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

>>>>

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\chaptermark{Fault Tolerant Circuit}
\section{Traces and circuit equivalence}
We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.  Due to the asynchronous nature of how signals are processed, each resulting half circuits may have signals of corresponding wires at different values.  To solve this problem we add C-elements to synchronize the two versions of the same signal.   An example of this transformation applied to the simple inverter circuit is shown in figure \ref{fig:dupschemeex}.  Both the duplication and the additional C-elements configuration are shown.  In the rest of this chapter we define a way to compare two circuits and to show their equivalence.  Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.  Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\
\begin{figure}
  \centering
    \includegraphics[width=.9\textwidth]{transf3Csimp}
  \caption{a) original circuit b) after the fault tolerant transformation}
  \label{fig:dupschemeex}
\end{figure}

Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially to evaluate whether they implement the same state graph.  
We first define a {\em trace}, to describe a path the circuit can take as it follows the state graph.  Different paths can occur because each state may have multiple alternative transitions from that state.  We record the succession of states and transitions by the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of finite or infinite length and $s_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: 0,\ldots ,n-1 \to S$ and $n \in \mathbb{N}$.
 Also every pair of consecutive states are transitions such that $T(s_i,s_{i+1})$ for $ 0\leq i\leq n-2$.  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
Thus a circuit has a set of traces.  
For a given circuit there is also a set of initial states from the set of traces which corresponds to the states in the state graph.  In other words, for all $s_0$, the first state of a trace of the circuit, $s\in S$.  \\

%Note that our definition of trace also includes the case where there is only one transition from each state of a state graph, which results in a linear state graph.

\begin{figure}
  \centering
    \includegraphics[width=.6\textwidth]{sm_counter2}
  \caption{a) original circuit for wire w b) an erroneous initialization}
  \label{fig:sm_counter2}
\end{figure}

The original circuit is semi-modular by design.  But the design only covers cases where the wires are in a state in the state graph.  That is, hazards may occur if the state of the circuit goes into an unreachable state of the state graph and the circuit is no longer semi-modular and furthermore becomes unpredictable.  This will not happen in the fault-free case if the circuit is initialized to a state in the state graph and the wires inside the logic blocks are properly initialized.  However it is a possibility when faults do occur and a reason why we need to transform the circuit to protect against faults.  An example of what might happen when the circuit is not in a semi-modular state is shown in figure \ref{fig:sm_counter2}.  The circuit for wire $w$ is taken out of a semi-modular circuit.  However, if the state of the $w,x,y,z$ wires are $(0,1,0,1)$ and the internal wires after the AND and OR gate are both initialized to 1, this is not a semi-modularity consistent initialization.  The output wire $w$ is excited to 1 while the inputs from $x,y,z$ will cause $w$ to transition to 0.  Depending on the timing of the gates, $w$ may stay at 0 or experience a glitch to 1 then back to 0.  The extra layers of gates in the logic block can be thought of as extra delays that can store and propagate the wrong values.  More detailed discussion of how to initialize the circuit will be explored after we define the fault tolerant transformation.\\

Given two circuits, how can we determine when their basic functionality is the same, especially if they are implemented with different gates and circuit elements?  We define a notion of equivalence between two circuits through their sets of traces.  
%We want the underlying state graph representation of the circuits to be equivalent.  However only the signals and the sequence of transitions from the circuit is observable.  In other words the trace is observable.  Thus we define circuits as equivalent if the set of traces of the two circuits are the same. [We use the assumption that if the set of traces are equal then the state graph is equal.]
\begin{definition} Two circuits A and B are {\em equivalent} if the set of all traces from circuit A is equal to circuit B.  In other words, $\{\sigma^A |\sigma^A$ is a possible trace in $A\}=\{\sigma^B |\sigma^B$ is a possible trace in $B\}$.
\end{definition}

We are now ready to explore how to make a circuit fault-tolerant.
%good enough for now, do I need if and only if? <-NO, xxx if xxx in math lingo is iff

@@

We can make an existing semi-modular circuit fault-tolerant by the following transformation as shown in \ref{fig:dupscheme}: make a duplicate copy of the logic blocks of each wire $w$ and label the duplicate wires $w^A$ and $w^B$.  We also label the duplicated logic blocks as belonging to circuit A or circuit B.  Then we connect the output of the logic blocks to three layers of C-elements as shown in figure \ref{fig:dupscheme}.  We label the intermediate wires as $c1^A$, $c2^A$, $c3^A$ for circuit A and $c1^B$, $c2^B$, $c3^B$ for circuit B.  In the first layer of C-elements, $c1^A$ and $c1^B$ are outputs of the logic blocks and inputs to two C-elements outputting $c2^A$ and $c2^B$.  These are then the inputs to the second layer of C-elements outputting $c3^A$ and $c3^B$.  These are then the inputs to the third layer of C-elements outputting $w^A$ and $w^B$.  We can label one of the final C-element outputs as $w^A$ and the other output as $w^B$.  These then connect to other logic blocks in circuit A and circuit B respectively.  Note that at some steps of the labelling which side is A and B can be somewhat arbitrary because the outputs of pairs of C-elements with the same inputs are symmetric.  The symmetry is broken by connecting the final output $w^A$ to all its circuit A gate inputs and $w^B$ to all its circuit B gate inputs.  All circuit elements with the A label is part of the A-half circuit and all circuit elements with the B label is part of the B-half circuit.\\%(Note that the outputs of the C-elements can be arbitrarily named and connected to the next gates, and the next gates can also be arbitrarily named $A$ or $B$ as long as it does not create any inconsistencies in the naming convention, ie. all $A$ wires feed into the $A$ gates)  %the only wires that really matter are the wires that have isochronic forks, these must input to same A or B, everything else is just a naming difference
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{circuitforproof3}
  \caption{Fault tolerant transformation: duplicate the original logic for each output wire and adding 3 layers of C-elements}
  \label{fig:dupscheme}
\end{figure}

We want to show that a half circuit of the fault tolerant circuit is functioning correctly.  To do this, we define a correspondence between states of the original circuit and states of the fault tolerant circuit.  As a result of the circuit transformation, a state of the fault tolerant circuit has bits for 8 times as many wires as a state in the original circuit.  Half of those bits are obviously from the A half of the circuit and half are from the B half.  The state graph for a fault tolerant circuit is defined on this combined state.  We define the half-circuit mapping $h^A: s^{\mathit{full}} \to s^A$ where $s^{\mathit{full}}$ is the combined state of a fault tolerant circuit and $s^A$ consists of wires $w^A$ that correspond to the original wires $w$ in the original duplication procedure.  The half-circuit mapping $h^B$ is similarly defined to map $s^{\mathit{full}}$ to $s^B$.  The added wires such as $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ from the duplication procedure are hidden by $h^A$ or $h^B$.  We extend $h^A$ to traces by using the following two steps: first, $h^A$ is applied individually to each state in a trace $\sigma$, and likewise for $h^B$.  %not sure if I want the mapping to be from variable to variable or specific state to state
%For a trace in the fault tolerant circuit we project the full states onto a shortened list of wires (ie the wires corresponding to the original circuit). 
The resulting trace may have successive repeated states.  So we delete all but one of the neighboring repeats to obtain a valid trace on the shortened list of wires.  The result should be a trace from the original circuit.
 Using this mapping we will show that the original circuit is equivalent to half of the fault tolerant circuit in both the absence and presence of a single transient fault.
%do I need to define all the new transitions in duplicated circuit?  maybe
\\

%[Why is this the best we can do?]
We compare to each half circuit because it is not easy to synchronize and compare the signals between the two halves, especially if we reuse the logic blocks from the original circuit.  A simple idea we tried was to insert another C-element before the input is fed into the logic, to synchronize the wires on both halves.  The problem with that is in the original circuit, a wire value change propagates to all inputs at the same time.  Adding another layer of C-elements create varying delays at the input to logic blocks and the isochronic fork assumption is violated.  Thus the resulting circuit will not function according to the specified state graph.  (an example can be provided but not sure if needed?)\\  
\begin{figure}
  \centering
    \includegraphics[width=.8\textwidth]{counterexhalf}
  \caption{State graph example to show how b can transition before a or c finishes in both halves in the fault tolerant circuit}
  \label{fig:counterexhalf}
\end{figure}

Next we look at the traces of each half circuit.  Figure \ref{fig:counterexhalf} shows a subsection of a semi-modular state graph where the states are given nominal names (state 0, state 1, ... etc) and each transition is labeled with the transitioning wire.  Suppose we apply our fault tolerant transformation to such a circuit based on this state graph.  Both halves will transition based on this state graph, with the added caveat that for a wire to transition in any one half, it must be excited in both halves at the current state.  Starting in {\em state 0} it is possible in the A-half for $a^A$ to transition to {\em state 1} and in the B-half for $c^B$ to transition to {\em state 2}.  We assume that $a^B$ and $c^A$ do not complete their transitions yet.  Immediately, in the A-half $b^A$ is excited and in the B-half $b^B$ is excited.  Then, suppose the transition on wire $b^A$ and $b^B$ occurs.  That is, the A-half transitions to {\em state 3} and the B-half transitions to {\em state 5}.  And finally, the excited $a^B$ and $c^A$ transitions so that both halves are in {\em state 6}.  The trace so far for the A-half is (state 0, state 1, state 3, state 6) while for the B-half it is (state 0, state 2, state 5, state 6).  Thus the two halves need not have the same trace.  The current fault tolerant transformation synchronizes the outputs of the logic blocks with C-elements.  If we want to reuse the same logic blocks but synchronize the signals earlier, such as replacing the final C-element in a standard C implementation with a 4C-element, the issue of different traces in the two halves will still occur.  This points to looking at properties of each half circuit as the right thing to do.\\

Another problem that the fault tolerant transformation cannot resolve is that if we take the following view for transitions, a transition of wire $w$ in the original circuit is complete if both $w^A$ and $w^B$ transitions in the fault tolerant circuit, then some signals may transition out of order.  We use the earlier example of figure \ref{fig:counterexhalf} to show this as well.  Following the same transitions outlined above, $b^A$ and $b^B$ can finish its transition before $a^B$ and $c^A$ transitions.  Then the $b+$ transition is actually completed before $a+$ or $c+$ and the combined state no longer maps back to a valid state in the original state graph.  Another approach we may take is to record the first transition of a wire in either half of the fault tolerant circuit.  For example if $w^A=w^B$ and then $w^A$ transitions, we map this to a transition on $w$ in the original circuit.  This approach ensures the resulting trace is a trace in the original circuit (can be shown by Lemma 1 and Lemma 2.1 in the next section) however, in the presence of faults, it is easy to see that it does not provide any fault tolerance.\\

For the aforementioned reasons, we choose to use the $h^A$ and $h^B$ mappings and compare each half circuit against the original circuit.  Out of the various comparisons methods and circuit transformations that we tried, it is the most reasonable and results in some nice properties.  We will next demonstrate that the half circuits are equivalent to the original circuit in the absence of faults.  Then we show that a similar property is true even when a single fault may occur.

\section{Normal operation analysis}
To prove claims about the fault tolerance of this circuit, we first prove that the circuit behaves similarly to the original circuit under normal operation.  That is, the set of traces of the fault tolerant circuit after applying a mapping of $h^A$ is equivalent to that of the original circuit.  And likewise after applying a mapping of $h^B$ to the fault tolerant circuit.  We show this through several Lemmas. Lemma 1 shows for each fault-free half of a circuit, if a transition occurs, it must be a transition in the state graph of the original circuit.  This is a strong result; it is true for arbitrary behavior of
signals in the other half circuit, so long as those signals are well formed Boolean values and also does not cause the fault-free half to deviate from well formed Boolean values.  
This result is also significant later in proving fault tolerance under a single transient fault since one of the halves is fault-free.  %as long as it does not violate digital abstraction
%One additional assumption that we make about the gates and wire values (including in the presence of faults) for Lemma 1 to hold is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.
\\

Note that Lemma 1 allows for the possiblity of deadlock.  Lemma 2 shows deadlock does not occur during normal operation.  Combining these two Lemmas, we can show that all traces in the duplicated circuit can be mapped to a trace in the original circuit.\\
% and all traces in the original can be mapped to duplicated after h mapping?  <-this is obvious though by setting the A half and B half to both transition according to original trace
%[so no deadlock in normal operation??]

Now we will discuss the proper wire initializations before going into the Lemmas.  In normal operation, the fault tolerant circuit must have wire values consistent with semi-modular behavior in the original circuit.  
This includes the internal wires which exist in the logic blocks in the original circuit and through duplication also exist in the fault tolerant circuit.  The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.  This arises from the original synthesis method to synthesize the circuit from an underlying state graph.  
Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.  The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.  Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.  %maybe needs an example
Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.  Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions. \\%newly added

What values to initialize the wires of a circuit to is very important.  We want certain properties to hold for all states that the circuit goes through, and such properties must also hold for the initial state.  On one hand, the initial state $s$ must be a state in the underlying state graph.  Thus the wire values is initialized to be consistent with that property.  On the other hand, as mentioned previously, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.  We assume that we can initialize the wire values of the original circuit to satisfy these two properties.  Given this, we pick convenient initializations for the fault tolerant circuit.  The following procedure covers how to initialize both the wires from the duplication as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.  The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s. The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.  Given these we will show how to define a corresponding initial state in the duplicated circuit.  %should I delete intermediate?
\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed as follows.  Given any state in the original circuit state graph $s \in S$, assume that there exists initial wire values that correspond to $s$.  In addition, for each wire $w$, the internal wire values within the logic block of $w$ are semi-modularity consistent.  Construct the valid initial state by copying the internal wire values to corresponding internal wires in the A half circuit.  Then assign the value $w$ to appropriate wires in the A half circuit such as $w=c1^A=c2^A=c3^A=w^A$. The same construction can be applied for the B half circuit as well.
\end{definition}
%\textbf{
This is one out of many possible initializations that can fit the behavior we want.  Thus this definition is stronger than it needs to be but is used for the sake of conveniece.  In Lemma 1, we will show why this definition allows for the behavior that we want in the fault tolerant circuit.\\

To avoid overly clunky sentences, we will assume that fault tolerant circuits start from the same valid intial state in both halves.  One exception to this assumption is Lemma 1 where only one half circuit is needed to start from a valid initial state since the property is true regardless of the wire values of the other half.\\ 
%For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.  I will not include this assumption in the following lemma definitions to avoid complicated wording.  %}  
%The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\

This leads to the definition and proof of Lemma 1 as follows:

\begin{lemma}[1]
If $\sigma$ is the trace of the fault tolerant circuit and the A half is fault free, then in the A half:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, a wire $w$ in state $h^A(s)$ is excited in the original circuit if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ in the fault tolerant circuit.  (No more than one of the four conditions mentioned may be true regardless if $w$ is excited or unexcited.)  A wire $w$ in $h^A(s)$ is unexcited in the original circuit if and only if none of the four conditions are true in the fault tolerant circuit.
\end{itemize}

%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
By symmetry this is also true for the B half if we exchange A and B in the statement above.

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
The trace $\sigma$ can be finite or infinite in length in accordance with the definition of a trace. 
\begin{proof}
We prove this Lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
\begin{itemize}
\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  Also a wire $w$ is unexcited if and only if none of the four excited conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.  This case can also interpreted as the logic block being excited.  Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.  As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.  By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.  This shows the valid initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}
